

```{r,echo=FALSE , error = TRUE}
    p<-chat2()[,2]%>% as.factor()%>%levels()%>%unique()
    paste(p[1],"'s"," chat with ",p[2], sep = "")%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Total Word Count", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>% as.data.frame()
    p<-chat_word_count(p$text)
    as.character(p)%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Total Letter Count", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>% as.data.frame()
    p<-chat_letter_count(p$text)
    as.character(p)%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Total Message Count", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>% as.data.frame()
    p<-chat_message_count(p$text)
    as.character(p)%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Total Chat Days", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>% as.data.frame()
    p<-chat_total_days(p$V1)
    as.character(p)%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Total Media shared with each other", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>% as.data.frame()
    p<-chat_media_items(p)
    if(is.data.frame(p)){
    p<-sum(p$Frequency)
    as.character(p)%>%h3(align = "center", style= "color:blue")%>%em()
    } else {
      paste("No Media Detected")%>%h3(align = "center", style= "color:blue")%>%em()
    }
```

`r hr()`

`r h3("Most Active Day", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>% as.data.frame()
    p<-chat_most_active(p$V1)
    p%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Leading Message Sender", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>% as.data.frame()
    p<-chat_name_freq_pie(p)
    paste(
    p[order(p[,2],decreasing = T)[1],1],"#Messages",
    p[order(p[,2],decreasing = T)[1],2])%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Most Used Emoji", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>%as.data.frame()
    p<-chat_emoji_with_freq(p$text)
    if(is.data.frame(p)){
    paste(p[1,1],p[1,2],"times",p[1,3])%>%h3(align = "center", style= "color:blue")%>%em()
    } else {
      p%>%h3(align = "center", style= "color:blue")%>%em()
    }
```

`r hr()`

`r h3("Words Typed Per Message", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>%as.data.frame()
    p<-chat_words_per_message(p$text)
    paste("No. of words,", p)%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Letters Typed Per Message", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>%as.data.frame()
    p<-chat_letters_per_message(p$text)
    paste("No. of letters,", p)%>%h3(align = "center", style= "color:blue")%>%em()
```

`r hr()`

`r h3("Messages Sent \nand\n Received Per Day", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>%as.data.frame()
    p<-chat_message_per_day(p$V1)
    paste("No. of messages,", p)%>%h3(align = "center", style= "color:blue")%>%em()
```
`r hr()`

`r h3("Letters Typed Per Day", style = "color:skyblue")`
```{r,echo=FALSE , error = TRUE}
p<-chat2()%>%as.data.frame()
    p<-chat_letter_per_day(p)
    paste(p,"letters inclusive of whitespaces")%>%h3(align = "center", style= "color:blue")%>%em()
```
`r hr()`

`r h3("No. of Messages by Individual", style = "color:skyblue")`
```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>%as.data.frame()
    plot_ly(chat_name_freq_pie(p), labels = ~Name, values = ~Frequency, type = 'pie',
            textposition = 'inside',
            textinfo = 'label+percent',
            insidetextfont = list(color = '#FFFFFF'),
            hoverinfo = 'text',
            text = ~paste('#', Frequency, ' Messages'),
            marker = list(colors = sample(brewer.pal(5, "Paired")),
                          line = list(color = '#362828', width = 1)),
            pull = 0.025,
            showlegend = FALSE) %>%
      layout(title = 'No. Of Messages by individual')
```

`r hr()`

`r h3("No. of Messages across Dayshifts", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>% as.data.frame()
    p<-chat_mshift_freq_pie(p)
      plot_ly(p, x= ~factor(V1, levels = unique(V1)),
            y= ~as.numeric(V2), type = 'bar', name = 'dayshifts', 
            marker = list(color = sample(brewer.pal(4,"Set2"))))%>% 
      layout(title = 'Overall distribution of messages\nacross dayshifts\n',
             xaxis = list(
               title = "Day Shifts"),
             yaxis = list(
               title = "No. of messages"),
             legend = list(x=0 , y = 0, barmode = 'group'
             ))
```

`r hr()`

`r h3("#Messages Distribution Over Weekdays", style = "color:skyblue")`
```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>% as.data.frame()
    p<-chat_weekdays_freq_pie(p)
    plot_ly(p, x= ~factor(V1, levels = unique(V1)), y = ~as.numeric(V2), type= 'bar',
            name = '#no. of messages', marker = list(color = sample(brewer.pal(7,"Set2"))))%>%
      layout(title = 'Overall message distribuition \nover weekdays\n',
             xaxis = list(
               title = "Weekdays->",
               tickfont = list(
                 size = 14,
                 color = 'rgb(107, 107, 107)')),
             yaxis = list(
               title = '# of messages',
               titlefont = list(
                 size = 16,
                 color = 'rgb(107, 107, 107)'),
               tickfont = list(
                 size = 16,
                 color = 'rgb(107, 107, 107)')),
             legend = list(x = 0, y = 0, bgcolor = 'rgba(255, 255, 255, 0)', bordercolor = 'rgba(255, 255, 255, 0)'),
             barmode = 'group', bargap = 0.15)
```

`r hr()`

`r h3("No. of Words By Individual", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>% as.data.frame()
    plot_ly(chat_word_freq_pie(p), labels = ~Name, values = ~Frequency, type = 'pie',
            textposition = 'inside',
            textinfo = 'label+percent',
            insidetextfont = list(color = '#FFFFFF'),
            hoverinfo = 'text',
            text = ~paste('#', Frequency, ' words'),
            marker = list(colors = sample(brewer.pal(7,"Set2")),
                          line = list(color = '#362828', width = 1)),
            pull = 0.025,
            showlegend = FALSE) %>%
      layout(title = 'No. Of words \nby individual')
```

`r hr()`

`r h3("No. of Letters By Individual", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>% as.data.frame()
    plot_ly(chat_letter_freq_pie(p), labels = ~Name, values = ~Frequency, type = 'pie',
            textposition = 'inside',
            textinfo = 'label+percent',
            insidetextfont = list(color = '#FFFFFF'),
            hoverinfo = 'text',
            text = ~paste('#', Frequency, ' Letters'),
            marker = list(colors = sample(brewer.pal(7,"Set2")),
                          line = list(color = '#362828', width = 1)),
            pull = 0.025,
            showlegend = FALSE) %>%
      layout(title = 'No. Of letters \nby individual')
```

`r hr()`

`r h3("Top 10 Emoji Distribution", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>%as.data.frame()
    chat_emoji_with_freq(p$text)[1:10,] %>%
      plot_ly(labels = ~Name, values = ~Frequency,
              textinfo = 'label',
              hoverinfo = 'label+text+percent',
              text = ~paste('#', Frequency, emo_name),
              marker = list(colors = c(brewer.pal(9, "Oranges")[seq(5,1)],brewer.pal(9, "PuOr")[c(4,3,5:7)]))) %>%
      add_pie(hole = 0.5,pull = 0.025) %>%
      layout(title = "Top 10 Emoji Used",  showlegend = F,
             xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
             yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

`r hr()`

`r h3("Average Wordlength by Individual", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
p<-chat2()%>% as.data.frame()
    plot_ly(data = chat_avg_ppwordl_freq_pie(p), labels = ~Name, values = ~Frequency, type = 'pie',
            textposition = 'inside',
            textinfo = 'label+percent',
            hoverinfo = 'text',
            text = ~paste('Avg wordlength', Frequency),
            marker = list(colors = brewer.pal(5,"Set3")%>%sample(),
                          line = list(color = '#362828', width = 1)),
            pull = 0.025
    )%>% layout(title = "Average wordlength \nby individual")
```

`r hr()`

`r h3("Distribution Of #Messages over\n24 Hours of the Day", style = "color:skyblue")`

```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>% as.data.frame()
    chat_over_24_hours(p)%>%
      plot_ly(x=~Var1, y = ~Freq, color = ~Var2,colors = sample(brewer.pal(3, "Dark2"))[1:2],type = "bar")%>%
      layout(title = "#Messages over 24 hours\nof the day",
             xaxis= list(
               title = "Hours of day ->"),
             yaxis = list(
               title = "No. of Messages\n "
             ),
             legend = list(x=0,y=1))
```
`r hr()`

`r h3("Conversation Starter\n", style = "color:skyblue")`
`r paste("Taking Time Consideration of", input$tconsider, "hours")%>%h4(style= "color:grey", align = "right")%>%em()`

```{r,echo=FALSE , error = TRUE}
    p<-chat2()%>% as.data.frame()
    plot_ly(chat_convo_starter(p,(input$tconsider)*3600),labels= ~Name, values =~Frequency, type = 'pie',
            textposition = 'inside',
            textinfo = 'label+percent',
            insidetextfont = list(color = '#FFFFFF'),
            hoverinfo = 'text',
            text = ~paste('#', Frequency,' times'),
            marker = list(colors = sample(brewer.pal(5,"Dark2")),
                          line = list(color = '#362828', width = 1)),
            pull = 0.025,
            showlegend = T) %>%
      layout(title = paste('Conversation starter'))
```

`r hr()`

`r h3("Longest Conversation\n", style = "color:skyblue")`
`r paste("Taking Max Halt Of", input$tconsider.convo, "minutes")%>%h4(style= "color:grey", align = "right")%>%em()`


```{r,echo=FALSE , error = TRUE}
 p<-chat2()%>% as.data.frame()
    chat_continue_conversation(p,((input$tconsider.convo)*60))%>%h3(style= "color:blue")%>%em()
```

`r hr()`

`r h3("Wordcloud\n", style = "color:skyblue")`
`r paste(input$cloudof)%>%toupper()%>%h4(style= "color:grey", align = "right")`

```{r wordcloud, echo=FALSE,fig.width = 8, fig.height= 8 , error = TRUE}
 v<-terms1()
    Frequency_index <- v>=input$minfreq
    Frequency<- v[Frequency_index]
    Word<- names(v)[Frequency_index]
    df<-data.frame(word = Word, freq= Frequency)
    df<-df[1:input$maxwords,]
    wordcloud2(data = df,
               size = input$size/100,fontFamily = input$font,fontWeight = input$fontweight,
               shape = input$shape, minRotation = pi/2,maxRotation =pi/2,
               backgroundColor = "black",color = "random-light")
```
`r hr()`

`r h3("First 10 Chat Messages", style = "color:skyblue")`

```{r, echo=FALSE , error = TRUE}
p<-chat2()%>%as.data.frame()
names(p)<-c("Date&time", "Participant", "Text")
pander(p[1:10,])
```
`r hr()`
